The Error Estimate of Force Calculation in the Heterogeneous Molecular Systems

### 2011-09-27 shortRange.inhomo/writeDown/main.tex
finish intro

In this work, we develop the error estimate of the short-range force
in inhomogeneous systems. The force error can be split into the
homogeneous and inhomogeneous part regardless the correlation in the
system. The inhomogeneous error that can be more than one order of
maganitude larger than the homogeneous error plays a dominant role in
the interfacial region. An adaptive cut-off method is hereby proposed
to equally distribte the error according to the error estimate, so
that a substantial computational effort can be saved while the
precision of simulation is preserved. We also proposed a long-range
force correction method based on the error estimate to screen out the
contribution of the inhomogeneous error, which can tremendously
improve the precision of simulation. To show the effectiveness of the
error estimate and the proposed methods, two systems are tested: the
liquid-vapor equilibrium for equilibrium properties, and the colliding
nanoscale clusters for dynamical properties. Finally, a conclusion is
given in section \ref{sec:conclusion}.

@@

\begin{table}
  \centering
  \caption{
    The maximum RMS force error and computational cost of 
    of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (FC) method.
    The computational cost is the number of pairwise interaction 
    measurements performed by the program, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
    & 5.0 &\textrm{ARC} & $9.2\times 10^{-3}$ & 2.9 \\
    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
  \end{tabular*}
\end{table}

@@

\section{Conclusion}\label{sec:conclusion}

>>>>

In this work, we develop the error estimate of the short-range force
in inhomogeneous systems. The force error can be split into the
homogeneous and inhomogeneous part regardless the particle-particle
correlation outside the cut-off radius. The inhomogeneous error that
can be more than one order of maganitude larger than the homogeneous
error plays a dominant role in the interfacial region. An adaptive
cut-off method is hereby proposed to equally distribte the error
according to the error estimate, so that a substantial computational
effort can be saved while the precision of simulation is preserved. We
also proposed a long-range force correction method based on the error
estimate to screen out the contribution of the inhomogeneous error,
which can tremendously improve the precision of simulation. To show
the effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties. Finally, conclusions are given in section
\ref{sec:conclusion}.

@@

\begin{table}
  \centering
  \caption{
    The maximum RMS force error and computational cost of 
    of three methods, namely the uniform cut-off
    (URC), the adaptive cut-off (ARC) and the force correction (FC) method.
    The computational cost is the number of pairwise interaction 
    measurements performed by the program, which should be mashine-independent.
  }\label{tab:tmp1}
  \begin{tabular*}{0.50\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.4 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-2}$ & 7.9 \\
    & 5.0 &\textrm{ARC} & $2.4\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $2.0\times 10^{-3}$ & 8.8 \\\cline{2-5}
    &     &\textrm{URC} & $4.9\times 10^{-3}$ & 27 \\
0.70& 7.5 &\textrm{ARC} & $4.9\times 10^{-3}$ & 13 \\
    &     &\textrm{FC } & $2.5\times 10^{-4}$ & 27 \\\cline{2-5}
    &     &\textrm{URC} & $1.6\times 10^{-3}$ & 59 \\
    &10.0 &\textrm{ARC} & $1.6\times 10^{-3}$ & 29 \\
    &     &\textrm{FC } & $5.8\times 10^{-5}$ & 59 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.4\times 10^{-2}$ & 3.1 \\\cline{2-5}
    &     &\textrm{URC} & $2.1\times 10^{-2}$ & 7.1 \\
    & 5.0 &\textrm{ARC} & $1.8\times 10^{-2}$ & 4.6 \\
    &     &\textrm{FC } & $1.9\times 10^{-3}$ & 7.9 \\\cline{2-5}
    &     &\textrm{URC} & $4.4\times 10^{-3}$ & 24 \\
0.85& 7.5 &\textrm{ARC} & $4.3\times 10^{-3}$ & 12 \\
    &     &\textrm{FC } & $3.0\times 10^{-4}$ & 24 \\\cline{2-5}
    &     &\textrm{URC} & $1.4\times 10^{-3}$ & 53 \\
    &10.0 &\textrm{ARC} & $1.4\times 10^{-3}$ & 26 \\
    &     &\textrm{FC } & $5.3\times 10^{-5}$ & 53 \\ \hline\hline
  \end{tabular*}
  \begin{tabular*}{0.49\textwidth}{c|c|@{\extracolsep{\fill}}ccc}\hline\hline
    $T^\ast$ &$r^\ast_{c}$ & \textrm{method} & $\max\mathcal E^\ast$ & Cost($\times 10^{-6}$) \\ \hline
    & 3.5 &\textrm{FC } & $1.3\times 10^{-2}$ & 3.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.5\times 10^{-2}$ & 5.6 \\
    & 5.0 &\textrm{ARC} & $1.5\times 10^{-2}$ & 3.2 \\
    &     &\textrm{FC } & $1.7\times 10^{-3}$ & 9.9 \\\cline{2-5}
    &     &\textrm{URC} & $3.3\times 10^{-3}$ & 17 \\
1.10& 7.5 &\textrm{ARC} & $3.5\times 10^{-3}$ & 8.8 \\
    &     &\textrm{FC } & $1.8\times 10^{-4}$ & 18 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-3}$ & 39 \\
    &10.0 &\textrm{ARC} & $1.0\times 10^{-3}$ & 19 \\
    &     &\textrm{FC } & $4.2\times 10^{-5}$ & 39 \\ \hline\hline
    & 3.5 &\textrm{FC } & $1.2\times 10^{-2}$ & 1.8 \\\cline{2-5}
    &     &\textrm{URC} & $1.1\times 10^{-2}$ & 4.2 \\
    & 5.0 &\textrm{ARC} & $1.0\times 10^{-2}$ & 2.8 \\
    &     &\textrm{FC } & $1.5\times 10^{-3}$ & 4.6 \\\cline{2-5}
    &     &\textrm{URC} & $2.5\times 10^{-3}$ & 14 \\
1.20& 7.5 &\textrm{ARC} & $2.4\times 10^{-3}$ & 7.7 \\
    &     &\textrm{FC } & $1.5\times 10^{-4}$ & 14 \\\cline{2-5}
    &     &\textrm{URC} & $8.2\times 10^{-4}$ & 30 \\
    &10.0 &\textrm{ARC} & $8.3\times 10^{-4}$ & 17 \\
    &     &\textrm{FC } & $3.3\times 10^{-5}$ & 31 \\\hline\hline
  \end{tabular*}
\end{table}

@@

\section{Conclusions}\label{sec:conclusion}
